---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# browserhistory

<!-- badges: start -->
[![R-CMD-check](https://github.com/stibu81/browserhistory/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/stibu81/browserhistory/actions/workflows/R-CMD-check.yaml)
[![Codecov test
coverage](https://codecov.io/gh/stibu81/browserhistory/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stibu81/browserhistory?branch=main)
<!-- badges: end -->

browserhistory offers tools to read and analyse the browser history of
Firefox with R. Support for other browsers might be added in the future.


## Installation

You can install the development version of browserhistory from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stibu81/browserhistory")
```

## Reading the Browser History

Firefox stores the browser history in a SQLite database called `places.sqlite`.
The function `read_firefox_history()` reads the browser history from this
database and returns it as a tibble. The package contains a small example
database that is read in the following example:

```{r}
library(browserhistory)
root_dir <- get_test_root_dir()
history <- read_browser_history(root_dir = root_dir)
history
```

In order to read the history, you need to figure out where Firefox stores the
relevant files. The folder contains a file called `profiles.ini` and subfolders
for one or more profiles. Use the folder that  contains `profiles.ini` as
the root directory. In the case of the test data contained in browserhistory,
the structure is as follows:

```{r}
list.files(root_dir, recursive = TRUE)
```

`read_firefox_history()` will automatically select the
default profiles, but when there are several profiles and you want to read
a different one, you have to pass the name of the profile folder to the
`profile` argument as follows:

```{r}
history <- read_browser_history(root_dir = root_dir, profile = "test_profile")
history
```

The following list gives hints on where to find the root directory on a small
number of systems:

* **Ubuntu 20.04/22.04:** If Firefox has been installed from a deb package, the root
  directory is `⁠~/.mozilla/firefox`. (This might also be true for other
  Debian-based distributions.) If Firefox has been installed as a snap package,
  the root directory is `⁠~/snap/firefox/common/.mozilla/firefox`⁠.
* **Windows 10/11:** The root directory is
  `⁠C:\Users\<username>\AppData\Roaming\Mozilla\Firefox`, where
  `<username>` must be replaced by your user name.
  

